### 2014-12-13 paper.tex
Minor changes to computing compactness

  We used a number of metrics to measure the compactness of districts.  To compute them, we used the geographic data from the U.S.~Census's TIGER/Line database~\cite{censustiger} on the shapes of congressional districts and census blocks, and where applicable, population data from the 2010~Census~\cite{census2010}.

@@

  %TODO: possibly reorganize this subsection once Miriam adds her parts

  With the non-population-based metrics especially, Alaska and Hawaii would present particular difficulties, since they include a number of widely dispersed islands.  However, Alaska has only one representative, and Hawaii only two, so since our analysis focused on states with at least three districts, we did not attempt to resolve these issues.

>>>>

  We used a number of the metrics discussed in Section~\ref{background} to measure the compactness of districts.  To compute them, we used the geographic data from the U.S.~Census's TIGER/Line database~\cite{censustiger} on the shapes of congressional districts and census blocks, and where applicable, population data from the 2010~Census~\cite{census2010}.

@@

  With the non-population-based metrics especially, Alaska and Hawaii present particular difficulties, since they include a number of widely dispersed islands.  However, Alaska has only one representative, and Hawaii only two, so since our analysis focused on states with at least three districts, we did not attempt to resolve these issues.
